DESIGN OF A TWO-PIECE BRASSIERE CUP TO FIT BREAST DATA POINTS TOWARD ITS AUTOMATION

### 2020-11-15 template/paper/paper_e.tex
Done-

%Authors: Please copy the abstract of your paper.
\abstract{
       A method to design the two-dimensional shapes of patterns of two piece brassiere cup is proposed when its target three-dimensional shape is given as a cloud of its data points. A brassiere cup consists of several patterns and their shapes are designed by repeatedly making a paper cup model and checking its three-dimensional shape. For improvement of design efficiency of brassieres, such trial and error must be reduced. As a cup model for check is made of paper not cloth, it is assumed that the surface of the model is composed of several developable surfaces. When two lines lying on a developable surface are given, the shape of the surface can be determined. Then, the two-piece brassiere cup can be designed by minimizing the error between the surface and given data points. It was mathematically verified that the original developable surface can be reproduced from data points on it by use of our proposed method.
}

@@

Developable surfaces that can be unfolded into a plane without expanding and contracting are widely used from shipbuilding to manufacturing of clothing, which are suitable to representation of surfaces that can be made of leather, paper, and sheet metal. In such fields, it is very important to design the two-dimensional shapes of plates which can form the required three-dimensional shape by being bent and joined. In this paper, we focus on production of brassieres, which is related to design of two-dimensional shapes of plates. 
Brassieres are manufactured to meet various demands, such as to enhance a woman's breast size, to create cleavage, or to minimize breast movement. For this reason, the cup shape of a brassiere is very important when designing a brassiere. A brassiere cup is formed by several pieces of cloth called patterns and a wire. For example, as shown in \rfig{fig:patterns}, a two-piece brassiere cup is composed of the upper pattern, the lower pattern and the lower line.
\begin{figure}[h!]
	\centering
	\subfigure[upper pattern]{
		\includegraphics[width=0.45\columnwidth]{./figure/UpperPattern.eps}
		\label{fig:pattern_U}
	}
	\hfil
	\subfigure[lower pattern]{
		\includegraphics[width=0.45\columnwidth]{./figure/LowerPattern.eps}
		\label{fig:pattern_L}
	}
	\\
	\subfigure[lower line]{
		\includegraphics[width=0.35\columnwidth]{./figure/LowerWire.eps}
		\label{fig:Wire}
	}
	\caption{Parts of a two-piece brassiere cup}
	\label{fig:patterns}
\end{figure}
 And the cup has three curves and they are also very important to design. As shown in \rfig{fig:TwoCurves}, one is the wire line corresponding to the boundary between a breast and a body. Another is the ridge line of the cup corresponding to the outline of a bust on a transverse plane. The other is the upper line to connect a cup and shoulder strap.

%==============================================================%
In apparel industries, the form of a product is fixed by fashion designers and pattern makers. Fashion designers draw an image of the product and pattern makers determine the shapes of patterns to meet various demands of the ideal shape, which previously mentioned about a brassiere, and so on.
%%fig
\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.25]{./figure/Lines.eps}
	\caption{Expression of a wire line, a ridge line and an upper line}
	\label{fig:TwoCurves}
\end{figure}
The design process of a brassiere cup is shown in \rfig{fig:process}. In design cite, pattern makers first consider the functional requirement of a brassiere cup based on a breast shape, then determine the pattern shape. Since this design procedure cannot mainly be performed by CAD system but based on experience and intuition, they must check the shapes with a paper model of the cup and modify them repeatedly to realize the function. So, the situation may cause unnecessary repetition of modifying and checking pattern shapes. In order to improve the design efficiency of brassieres, it is required to reduce such trial and error as much as possible. So, in this paper, we focus on the process srrounded by a dotted line in \rfig{fig:process} and aim to automate it. 
When it comes to the function of a brassiere cup, Higuchi researched what emphasis is placed on in design of a brassiere cup\cite{c1}. According to  \cite{c1}, the function: fitting breast is most important. Therefore, we propose a method to design the shapes of patterns of a brassiere cup fitting the given breast shape. The given three-dimensional breast shape is assumed to be given as a cloud of data points, which can be obtained easily by measurement.

@@

%==============================================================%

As a cup shape is made by bending and sewing each pattern and assumed to be inextensible, the cup model consists of several developble surfaces.
With respect to modeling of develoable surfaces, a method to model developable surface by focusing on the geodesic line\cite{c2}, B-spline or NURBS surface\cite{c3,c4}, offsets of Bartrand curves which coincide each normal direction\cite{c5,c6}, and arbitrary curves on it\cite{c7}. Especially, Martin proposed a method to reconstruct developable surface from its point clouds based on Laguerre geometry\cite{c8}. Also, Chen et al. proposed an algorithm to approximate developable surface from its point cloud\cite{c9}. However, all of them does not reference its developed shape and only focus on a single developable surface. When it comes to manufacturing a brassiere cup, the pattern shapes, i.e. developed shapes of a cup is required, not 3D cup shape. Especially in a study on brassieres, Wakamatsu et al. proposed a method to predict the three-dimensional shape of a paper cup model when the two-dimensional shape of pattern is given \cite{c10,c11}. As a result, evaluation of the patterns becomes possible without actually creating a paper model. However, repetitive modification of the patterns is still required to obtain the target three-dimensional shape of the cup.
Ito et al. developed a paper model CAD system based on the theory of developable surfaces\cite{c12}. If a three-dimensional curve that means a sewn curve and a two-dimensional curve that means a piece to be sewn are given, a feasible region where the sewn surface does not intersect itself can be shown with this system. However, it is difficult to design the shape of patterns, that is, the shape of two-dimensional curves with this system.
We previously proposed method to design pattern shape and its developable surface from two lines: a wire line and a ridge line. They are obtained by solving optimization problem whose design parameters are the geodesic curvatures of a pattern shape and objective function is the error between generatrices determined by the geodesic curvature of a lower edge and the wire line and generatrices determined by the geodesic curvature of an upper edge and the ridge line. However, when it apply to this problem, it is required to  solve this optimization problem until the intended shape\cite{MyRef}. It leads to taking unnecessary time.
%==============================================================%

The products are mainly composed of two or three pieces of pattern. In this paper, we focus on two-piece brassiere cup and aim to propose a method to design its pattern shapes toward improvement of its design efficiency when a cloud of its data points is given.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{MODELING OF DEVELOPABLE SURFACE AND PATTERN SHAPE}

In this section, we aim to explain numerical expression of a developable surface. 
When it comes to a curvature of a space curve on a surface, it is divided to the normal curvature by deforming the surface and the geodesic curvature by deforming a space curve. The geodesic curvature does not change by deforming the surfce as long as it is not stretched. In case of a brassiere cup, the normal curvature can be manipulated by deforming the surface, but the geodesic curvature cannot. So, it is required to design the geodesic curvature in order to coincide a space curve with a boundary of the developable surface. Let \textit{lower edge} be the curve connecting to a lower wire as shown Fig.\ref{fig:pattern_L}, and \textit{upper edge} be the curve combining with upper cup as shown Fig.\ref{fig:pattern_L}. In this section, we aim to propose a method to determine a developable surface by two curves that lie on it and to design the pattern shape from them. We explain the method to express the developable surface from parameters of a space curve , the condition of two lines that lie on the developable surface, and a pattern shape obtained from them.
For this aim, we set object coordinate system on the lower edge of the cup surface as shown \rfig{fig:obj_coord} so that $\zeta$ -axis always coincides the tangential direction of the edge line and $\eta$ -axis always coincides the normal direction of the surface. The posture of the object coordinate system is changed by deformation of the cup. Then, the infinitesimal displacement vector of each axial direction can be described by the infinitesimal rotational ratio vector $ \mbold{\omega} = \left[\omega_{\xi}\;\;\omega_{\eta}\;\;\omega_{\zeta}\right]^{\mathrm{T}}$as follows:

\begin{equation}\label{eq:ObjSys}
\left[\begin{array}{ccc} \xivec' & \etavec' & \zetavec' \end{array}\right] = \left[\begin{array}{ccc} \xivec & \etavec & \zetavec \end{array} \right] \mbold{\Omega}(\mbold{\omega}), 
\end{equation}
where a prime means a derivative of $s$, and $\mbold{\Omega}(\mbold{\omega})$ is represented as follows: 
\begin{equation}
\mbold{\Omega}(\mbold{\omega}) = \left[\begin{array}{ccc}
0 &-\omega_{\zeta} & \omega_{\eta} \\
\omega_{\zeta} & 0 &-\omega_{\xi} \\
-\omega_{\eta} & \omega_{\xi} &0
\end{array}\right]. 
\end{equation}

Then, the tangent vector is expressed as follows: 
\begin{equation}
\zetavec(s) = \zetavec_0 + \int_{0}^{s} \left( \omega_{\eta} \xivec - \omega_{\xi} \etavec \right) ds,
\label{eq:zetav_eq}
\end{equation}
where $\zetavec_0$ represents the tangent vector at $s=0$ and by integrating \req{eq:zetav_eq}, the position of the curve can be calculated as follows:
\begin{equation}
\mbold{x}(s) = \mbold{x}_0 + \int_0^s \zetavec ds, 
\end{equation}
where $\mbold{x}_0$ means the position at $s=0$.

@@

First, we explain numerical expression of developable surface by the constraint of Gaussian curvature. 
In general, a normal curvature of a direction vector $\mbold{d}_{\theta} = \zetavec \cos \theta + \xivec \sin \theta $ can be described using coefficients of the first and the second fundamental forms $E, F, G, L, M$ and $N$:
\begin{equation}\label{eq:def_kappa_theta}
\kappa_{\theta} = \frac{L \cos^2 \theta + 2M \sin \theta \cos \theta + N \sin^2 \theta}{E \cos^2 \theta + 2F \sin \theta \cos \theta + G \sin^2 \theta}.
\end{equation}
And the Gaussian curvature $K$ and the mean curvature $H$, which characterize a surface, can be defined as extreme values of \req{eq:def_kappa_theta}: $ \kappa_{\max} $ and $ \kappa_{\min} $ as follows

@@

In this paper, coefficients of first fundamental form are represented as following equation:
\begin{equation}
E = \zetavec \cdot \zetavec = 1, F = \zetavec \cdot \xivec = 0, G = \xivec \cdot \xivec = 1.
\end{equation}
Also, coefficients of second fundamental form are represented as following equation:
\begin{equation}
L = \zetavec' \cdot \eta = -\omega_{\xi}, M = \xivec' \cdot \eta = -\omega_{\zeta}.
\end{equation}
Then, Gaussian curvature $K$ and the mean curvature $H$ are described by
the following equation:

\begin{eqnarray}
\label{eq:GC_expressed_omega}
K &=& -\omega_{\xi} N - \omega_{\zeta}^2, \\
H &=& \disfrac{-\omega_{\xi}+N}{2}.
\end{eqnarray}
Developable surface is defined as the surface whose Gaussian curvature $K = 0$, which means $\kappa_{\min}=0$. Then, the mean curvature can be calculated as $2H=\kappa_{\max}$. This means that a line direction of which coincides with direction $\mbold{d}_{\min}$ is kept straight after deformation. This straight line is referred to as a generatrix. 
In this paper, principal directions are described by using the angle $ \alpha $: 
\begin{eqnarray}\label{eq:d1d2_eq}
\mbold{d}_{\max} &=& \zetavec \cos \alpha + \xivec \sin \alpha, \nonumber \\ 
\mbold{d}_{\min} &=& -\zetavec \sin \alpha + \xivec \cos \alpha.
\end{eqnarray}
The angle $ \alpha $ is referred to as the \textit{rib angle} in this paper.
By solving $ \kappa_{\theta} = 0 $,　the rib angle $ \alpha $ can be calculated as following equation:
\begin{equation}\label{eq:alpha_eq}
\tan \alpha = -\frac{\omega_{\zeta}}{\omega_{\xi}}.
\end{equation}
And from \req{eq:GC_expressed_omega}, $\kappa_1$ is calculated as follows: 
\begin{equation}\label{eq:kappa1_eq}
\kappa_1 = -\frac{\omega_{\xi}^2 + \omega_{\zeta}^2}{\omega_{\xi}}.
\end{equation}
From above, a developable surface can be determined by $\mbold{\omega}$.
%%%%%%%%%%%%%%ここまで7/21

Next, we explain the constraint of developable surface when two curves that lie on the surface are given. Let $s_a$ and $s_b$ be the arc length and $\mbold{x}_a(s_a)$, $\mbold{x}_b(s_b)$ be positions of each curve. We assume that these curves have ${\rm C}^2$ community at least. In general developable surfaces are a special kind of ruled surfaces. When the surface is a ruled surface, a generatrix $ \mbold{g} $ is described as follows:

@@

Note that $s_a$ can take an arbitrary value against $ s_b $. Therefore, the variation of a generatrix $ \Delta \mbold{g} $ is described by total differential form as follows:
\begin{equation}
\Delta \mbold{g} = -\zetavec_a \Delta s_a + \zetavec_b \Delta s_b,
\end{equation}
where $ \zetavec_a$ and $\zetavec_b $ are tangent vectors of $ \mbold{x}_a $ and $ \mbold{x}_b $, respectively. Next, let $ \Theta $ be the infinitesimal plane surrounded by four vectors $ \zetavec_a \Delta s_a, \zetavec_b \Delta s_b,\mbold{g}$, and $\mbold{g}+\Delta \mbold{g} $ as shown in \rfig{fig:Theta}. When the ruled surface is a developable surface, the plane $ \Theta $ is a tangent plane without twisting. Therefore, it leads to following equation:
\begin{equation}
\det (\zetavec_a, \mbold{g}, \mbold{g}+\Delta \mbold{g})=0
\end{equation}
By solving it, the following equation is obtained:
\begin{equation}
\det (\zetavec_a, \zetavec_b, \mbold{g})=0
\label{eq:Cond1}
\end{equation}
\begin{figure}[!h]
	\centering
	\includegraphics[width = 0.8\columnwidth]{./figure/Theta.eps}
	\caption{Definition of $ \Theta $}
	\label{fig:Theta}
\end{figure}
It indicates that the arc length of each curve is subordination. When two curves are corresponded to edge lines and $s_b$ can be expressed as $s_b(s_a)$, $\mbold{d}_{\min}\equiv\frac{\mbold{g}}{|\mbold{g}|}$ is established. Then, a rib angle is calculated by \req{eq:d1d2_eq} as follows:
\begin{equation}
\alpha = -\sin^{-1}\left( \mbold{d}_{\min} \cdot \zetavec_a \right).
\end{equation}
Using $\mbold{d}_{\min}$ and $\alpha$, $\mbold{\omega}$ can be represented as following equation:
\begin{equation}\label{eq:omegaVec}
\mbold{\omega} = \left[\begin{array}{c} -\det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \\ \zetavec_a' \cdot \mbold{d}_{\min} \\ \det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \tan \alpha \end{array}\right] 
\end{equation}
Therefore, when two curves that lie on the surface are given, a developable surface can be determined.

Next, we explain how to determine the pattern shape from the developable surface. The planar curve generated by developing the space curve $ \mbold{x}_a $ is defined a the lower curve and that by developing the space $ \mbold{x}_b $ is defined as the upper curve.

>>>>

%Authors: Please copy the abstract of your paper.
\abstract{
       A brassiere cup consists of several patterns. Traditionally, it is designed by repeatedly creating a paper cup model and verifying its three-dimensional (3D) shape. Reducing such trial and error will enhance the design efficiency. A method to partly automate the design of two-dimensional shapes in the patterns for a two-piece brassiere cup is proposed when the target 3D shape is given as a cloud of data points. It is assumed that the surface of the model is composed of several developable surfaces because the model is made of paper and not cloth. If two lines lying on a developable surface are given, the shape of the surface can be determined. Consequently, a two-piece brassiere cup can be designed by minimizing the error between the surface and the given data points. Here, we mathematically verify that our proposed method can reproduce the original developable surface.
}

@@

Developable surfaces can be unfolded into a plane without expanding or contracting. They are widely used in many industries from shipbuilding to manufacturing of clothing because they can represent surfaces made of leather, paper, or sheet metal. It is important to design two-dimensional (2D) shapes that form the required three-dimensional (3D) shape by bending and joining. In this paper, we focus on production of brassieres, which is related to design of two-dimensional shapes of plates. 
Brassieres are manufactured to meet various demands, such as to Herein we focus on the production of brassieres, which is related to the design of 2D shapes of plates. Brassieres are manufactured to meet various demands such as enhancing a woman’s breast size, creating cleavage, or minimizing breast movement. Due to these diverse demands, the cup shape is a critical element when designing a brassiere. A brassiere cup is formed by several pieces of cloth called patterns and a wire. Figure 1 shows an example of a two-piece brassiere cup composed of an upper pattern, lower pattern, and lower line. 
\begin{figure}[h!]
	\centering
	\subfigure[upper pattern]{
		\includegraphics[width=0.45\columnwidth]{./figure/UpperPattern.eps}
		\label{fig:pattern_U}
	}
	\hfil
	\subfigure[lower pattern]{
		\includegraphics[width=0.45\columnwidth]{./figure/LowerPattern.eps}
		\label{fig:pattern_L}
	}
	\\
	\subfigure[lower line]{
		\includegraphics[width=0.35\columnwidth]{./figure/LowerWire.eps}
		\label{fig:Wire}
	}
	\caption{Parts of a two-piece brassiere cup}
	\label{fig:patterns}
\end{figure}
 The three resulting curves are important to the design. The wire line corresponds to the boundary between the breast and body (\rfig{fig:TwoCurves}). The ridge line of the cup corresponds to the outline of a bust on a transverse plane, while the upper line connects the cup to the shoulder strap.

%==============================================================%
In apparel industries, the form of a product is fixed by fashion designers and pattern makers. Fashion designers draw the product image, while pattern makers determine the pattern shapes to meet various demands of the ideal shape.
%%fig
\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.25]{./figure/Lines.eps}
	\caption{Expression of a wire line, a ridge line and an upper line}
	\label{fig:TwoCurves}
\end{figure}
\rfig{fig:process} overviews the design process of a brassiere cup. Pattern makers first consider the functional requirement of a brassiere cup based on the breast shape, and then they determine the pattern shape. This design process is based on experience and intuition. Hence, pattern makers must verify the shapes with a paper model of the cup and repeatedly modify the shapes to realize the intended function. This process may cause unnecessary repetition. To improve the design efficiency of brassieres, trial and error should be minimized. Herein we strive to automate the steps indicated by the dotted line in \rfig{fig:process}. 
A previous study on the influence of design on the function of a brassiere cup found that fitting the breast has the largest impact\cite{c1}. Hence, this study proposes a method to design the pattern shapes of a brassiere cup to fit the given breast shape. Here, the given 3D breast shape is assumed to be a cloud of data points, which can be obtained easily by measurements.

@@

%==============================================================%
Because the cup shape is made by bending and sewing each pattern and is assumed to be inextensible, a cup model consists of several developable surfaces. With respect to modeling of developable surfaces, previously proposed modeling methods have focused on the geodesic line\cite{c2}, B-spline or NURBS surface\cite{c3,c4}, offsets of Bertrand curves, which coincide with each normal direction\cite{c5,c6}, and arbitrary curves\cite{c7}. Martin proposed a method to reconstruct a developable surface from its point clouds based on the Laguerre geometry\cite{c8}. Chen et al. proposed an algorithm to approximate a developable surface from its point cloud\cite{c9}. However, none of these methods reference the developed shape as they focus on a single developable surface. Manufacturing of a brassiere cup requires the pattern shapes (i.e., developed shapes of a cup) but not the 3D cup shape.

In a study on brassieres, Wakamatsu et al. proposed a method to predict the 3D shape of a paper cup model when the 2D shape of a pattern is given\cite{c10,c11}. Hence, patterns can be evaluated without actually creating a paper model. However, repetitive modification of the pattern is still required to obtain the target 3D shape of the cup. Ito et al. developed a paper model CAD system based on the theory of developable surfaces\cite{c12}. If a 3D curve, which means a sewn curve, and a 2D curve, which means a piece to be sewn, are given, this system can identify the feasible region where the sewn surface does not intersect itself. Unfortunately, it is difficult to design the pattern shapes. That is, determining the shape of 2D curves is challenging with this system. 
We previously proposed a method to design the pattern shape and its developable surface from two lines: a wire line and a ridge line. These lines are obtained by solving the optimization problem when the design parameters are the geodesic curvatures of a pattern shape and the objective function is the error between generatrices determined by the geodesic curvature of a lower edge and the wire line and generatrices determined by the geodesic curvature of an upper edge and the ridge line. However, the previously proposed method requires an iterative process to solve the optimization problem for the intended shape\cite{c13}, which is time-consuming.
Brassiere patterns are typically comprised of two or three pieces. Herein we focus on a two-piece brassiere cup, and we propose a design method to improve the design efficiency when a cloud of its data points is given.

%==============================================================%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{MODELING OF DEVELOPABLE SURFACE AND PATTERN SHAPE}

This section explains the numerical expressions of a developable surface. The curvature of a space curve on a surface can be divided into two: the normal curvature and geodesic curvature. The former is realized by deforming the surface, while the latter is realized by deforming a space curve. Deforming the surface does not change the geodesic curvature as long as the surface is not stretched. In the case of a brassiere cup, only the normal curvature can be manipulated by deforming the surface. Because the geodesic curvature cannot be manipulated by deforming the surface, it must be designed such that the space curve coincides with a boundary of the developable surface. 
Here, we propose a method to determine a developable surface using two curves that lie on the surface and design a pattern shape. Consider the case where the \textit{lower edge} is the curve connecting the lower wire (\rfig{fig:pattern_L}) and the \textit{upper edge} is that combining the upper cup (\rfig{fig:pattern_U}). Our method expresses the developable surface using the parameters of a space curve, the condition of two lines that lie on the developable surface, and their obtained pattern shape. \rfig{fig:obj_coord} depicts the object coordinate system on the lower edge of the cup surface, where the $\zeta$-axis always coincides with the tangential direction of the edge line and the  $ \eta $-axis always coincides with the surface normal direction. Deformation of the cup changes the posture of the object coordinate system. Thus, the infinitesimal displacement vector of each axial direction can be described by the infinitesimal rotational ratio vector $ \mbold{\omega} = \left[\omega_{\xi}\;\;\omega_{\eta}\;\;\omega_{\zeta}\right]^{\mathrm{T}}$ as

\begin{equation}\label{eq:ObjSys}
\left[\begin{array}{ccc} \xivec' & \etavec' & \zetavec' \end{array}\right] = \left[\begin{array}{ccc} \xivec & \etavec & \zetavec \end{array} \right] \mbold{\Omega}(\mbold{\omega}), 
\end{equation}
where a prime means a derivative of $s$, and $\mbold{\Omega}(\mbold{\omega})$ is represented as
\begin{equation}
\mbold{\Omega}(\mbold{\omega}) = \left[\begin{array}{ccc}
0 &-\omega_{\zeta} & \omega_{\eta} \\
\omega_{\zeta} & 0 &-\omega_{\xi} \\
-\omega_{\eta} & \omega_{\xi} &0
\end{array}\right]. 
\end{equation}

Then, the tangent vector is expressed as 
\begin{equation}
\zetavec(s) = \zetavec_0 + \int_{0}^{s} \left( \omega_{\eta} \xivec - \omega_{\xi} \etavec \right) ds,
\label{eq:zetav_eq}
\end{equation}
where $\zetavec_0$ represents the tangent vector at $s=0$. By integrating \req{eq:zetav_eq}, the position of the curve can be calculated as
\begin{equation}
\mbold{x}(s) = \mbold{x}_0 + \int_0^s \zetavec ds, 
\end{equation}
where $\mbold{x}_0$ indicates the position at $s=0$.

@@

First, consider the numerical expression of a developable surface constrained by a Gaussian curvature. In general, the normal curvature of a direction vector $\mbold{d}_{\theta} = \zetavec \cos \theta + \xivec \sin \theta $ can be described using coefficients of the first and the second fundamental forms $E, F, G, L, M$ and $N$ as
\begin{equation}\label{eq:def_kappa_theta}
\kappa_{\theta} = \frac{L \cos^2 \theta + 2M \sin \theta \cos \theta + N \sin^2 \theta}{E \cos^2 \theta + 2F \sin \theta \cos \theta + G \sin^2 \theta}.
\end{equation}
Then the Gaussian curvature $K$ and the mean curvature $H$, which characterize a surface, can be defined as extreme values of \req{eq:def_kappa_theta}: $ \kappa_{\max} $ and $ \kappa_{\min} $ as

@@

Here, the coefficients of the first fundamental form are represented as
\begin{equation}
E = \zetavec \cdot \zetavec = 1, F = \zetavec \cdot \xivec = 0, G = \xivec \cdot \xivec = 1.
\end{equation}
In addition, the coefficients of the second fundamental form are represented as
\begin{equation}
L = \zetavec' \cdot \eta = -\omega_{\xi}, M = \xivec' \cdot \eta = -\omega_{\zeta}.
\end{equation}
Then Gaussian curvature $K$ and the mean curvature $H$ are described by the following equations

\begin{eqnarray}
\label{eq:GC_expressed_omega}
K &=& -\omega_{\xi} N - \omega_{\zeta}^2, \\
H &=& \disfrac{-\omega_{\xi}+N}{2}.
\end{eqnarray}
A developable surface is defined as a surface with a Gaussian curvature $K = 0$. That is $\kappa_{\min}=0$. TThus, the mean curvature can be calculated as $2H=\kappa_{\max}$. The line direction coinciding with the direction $\mbold{d}_{\min}$ remains straight after a deformation. This straight line is referred to as a generatrix. In this paper, the principal directions are described using the angle $ \alpha $ as 
\begin{eqnarray}\label{eq:d1d2_eq}
\mbold{d}_{\max} &=& \zetavec \cos \alpha + \xivec \sin \alpha, \nonumber \\ 
\mbold{d}_{\min} &=& -\zetavec \sin \alpha + \xivec \cos \alpha.
\end{eqnarray}
The angle $ \alpha $ is referred to as the \textit{rib angle} in this paper.
By solving $ \kappa_{\theta} = 0 $,　the rib angle $ \alpha $ can be calculated as
\begin{equation}\label{eq:alpha_eq}
\tan \alpha = -\frac{\omega_{\zeta}}{\omega_{\xi}}.
\end{equation}
From \req{eq:GC_expressed_omega}, $\kappa_1$ is calculated as 
\begin{equation}\label{eq:kappa1_eq}
\kappa_1 = -\frac{\omega_{\xi}^2 + \omega_{\zeta}^2}{\omega_{\xi}}.
\end{equation}
From above, a developable surface can be determined by $\mbold{\omega}$.
%%%%%%%%%%%%%%ここまで7/21

Next, consider the constraint of a developable surface when two curves lie on the surface. Let $s_a$ and $s_b$ be the arc length and $\mbold{x}_a(s_a)$, $\mbold{x}_b(s_b)$ be positions of each curve. We assume that these curves have ${\rm C}^2$ community at least. In general, developable surfaces are a special kind of ruled surface. When a surface is a ruled surface, the generatrix $ \mbold{g} $ is described as

@@

Note that $s_a$ can take an arbitrary value against $ s_b $. Therefore, the variation of a generatrix $ \Delta \mbold{g} $ is described by total differential form as
\begin{equation}
\Delta \mbold{g} = -\zetavec_a \Delta s_a + \zetavec_b \Delta s_b,
\end{equation}
where $ \zetavec_a$ and $\zetavec_b $ are tangent vectors of $ \mbold{x}_a $ and $ \mbold{x}_b $, respectively. Next, let $ \Theta $ be the infinitesimal plane surrounded by four vectors $ \zetavec_a \Delta s_a, \zetavec_b \Delta s_b,\mbold{g}$, and $\mbold{g}+\Delta \mbold{g} $ (\rfig{fig:Theta}). When the ruled surface is a developable surface, the plane $ \Theta $ is a tangent plane without twisting. Therefore, it leads to following equation:
\begin{equation}
\det (\zetavec_a, \mbold{g}, \mbold{g}+\Delta \mbold{g})=0
\label{eq:det_developeq}
\end{equation}
Solving \req{eq:det_developeq} gives
\begin{equation}
\det (\zetavec_a, \zetavec_b, \mbold{g})=0
\label{eq:Cond1}
\end{equation}
\begin{figure}[!h]
	\centering
	\includegraphics[width = 0.8\columnwidth]{./figure/Theta.eps}
	\caption{Definition of $ \Theta $}
	\label{fig:Theta}
\end{figure}
\req{eq:Cond1} indicates that the arc length of each curve is subordination. When two curves are corresponded to edge lines and $s_b$ can be expressed as $s_b(s_a)$, $\mbold{d}_{\min}\equiv\frac{\mbold{g}}{|\mbold{g}|}$ is established. Then, a rib angle is calculated by \req{eq:d1d2_eq} as follows:
\begin{equation}
\alpha = -\sin^{-1}\left( \mbold{d}_{\min} \cdot \zetavec_a \right).
\end{equation}
Using $\mbold{d}_{\min}$ and $\alpha$, $\mbold{\omega}$ can be represented as
\begin{equation}\label{eq:omegaVec}
\mbold{\omega} = \left[\begin{array}{c} -\det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \\ \zetavec_a' \cdot \mbold{d}_{\min} \\ \det(\zetavec_a',\zetavec_a, \mbold{d}_{\min} ) \tan \alpha \end{array}\right] 
\end{equation}
Therefore, when two curves that lie on the surface are given, a developable surface can be determined.

Now let’s consider how to determine the pattern shape from a developable surface. The planar curve generated by developing the space curve $ \mbold{x}_a $ is defined as the lower curve, whereas that generated by developing the space $ \mbold{x}_b $ is defined as the upper curve. \rfig{fig:PatternImage} shows the developed planar coordinate system $ vw $ so that $ v $-axis always coincides the line AB. Let $ \mu_a $ be the angle between the tangential direction of the lower edge and the $ v $-axis. 
If the curvature of the lower curve $ \omega_{\eta_a} $ is given, $ \mu_a $ is obtained as
\begin{equation}\label{eq:mu_eq}
\mu_a = \mu_0 + \int_{0}^{s_a} \omega_{\eta_a} ds_a,
\end{equation}
where $ \mu_0 $ represents the angle of the lower edge at $ s=0 $, which is discussed later. From \req{eq:mu_eq}, the planar position $ \mbold{x}_{ae} $ is described as
\begin{equation}\label{eq:x_LE}
\mbold{x}_{ae}  = \int_{0}^{s_a} \left[\begin{array}{cc} \cos \mu_a \\ \sin \mu_a \end{array}\right] ds_a
\end{equation}
With respect to \req{eq:mu_eq}, let $ a,b $ be defined as follows:
\begin{eqnarray}
a &=& \int_{0}^{L_a} \cos \left( \int_{0}^{s_a} \omega_{\eta_a} ds\right) ds_a, \\
b &=& \int_{0}^{L_a} \sin \left( \int_{0}^{s_a} \omega_{\eta_a} ds\right) ds_a. 
\end{eqnarray}
Then, $ \mu_0 $ can be calculated as follows:
\begin{equation}\label{eq:mu_0eq}
\mu_0 = \tan^{-1}\frac{b}{a}
\end{equation}
Let $ \mbold{x}_{be} $ be the planar position of an upper edge. Since the rib angle of a pattern $ \alpha_a $ and the length of a generatrix of a pattern $ |\mbold{g}| $ do not change by being developed, $ \mbold{x}_{be} $ can be calculated as 
\begin{equation}\label{eq:x_UE}
\mbold{x}_{be} = \mbold{x}_{ae} + |\mbold{g}| \left[\begin{array}{cc} \cos \left(\mu_a + \pi/2 + \alpha_a \right) \\ \sin \left(\mu_a + \pi/2 + \alpha_a \right)  \end{array}\right] 
\end{equation}
From above, a developed shape can be obtained when two curves, which lie on the developable surface, are given.
\begin{figure}[thpb]
	\centering
	\includegraphics[width = \columnwidth]{./figure/PatternImage2.eps}
	\caption{Description of pattern shape using geodesic curvature of the lower curve}
	\label{fig:PatternImage}
\end{figure}
\section*{EXPRESSION OF THE DESIGN PROCESS AS AN OPTIMIZATION PROBLEM}
From section 2, the cup shape can be determined by three curves: a wire line, a ridge line, and an upper line. If the wire line is given, designing the parameters for the ridge and upper lines such that the degree of fitting to the 3D breast shape is minimized will enhance the design efficiency. This section formulates the optimization problem that our proposed method aims to solve.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Formulation of the error between a point and a surface}
To formulate the degree of fitting to a 3D ideal shape, we formulate the error between a point and a surface. In general, the position $\mbold{X}(s,t)$ of a developable surface $S$ is expressed as
\begin{equation}\label{eq:Sur_eq}
\mbold{X}(s,t) = \mbold{x}(s) + t\mbold{d}_{\min}(s)
\end{equation}
The distance $\varepsilon(\mbold{p})$ between a point $\mbold{p}$ and a developable surface is formulated by the difference vector $\mbold{\delta}=\mbold{p}-\mbold{X}(s,t)$ as
\begin{equation}\label{eq:eps_eq}
\varepsilon(\mbold{p})=\min_{s,t}{|\mbold{\delta}|}
\end{equation}
When a set of surface parameters $ (s^*,t^*) $ satisfies to minimize \req{eq:eps_eq}, $\mbold{\delta}$ is parallel to $ \etavec $. Therefore, the following equations are satisfied
\begin{equation}\label{eq:d_mindoteq}
\mbold{d}_{\min} \cdot (\mbold{p} - \mbold{X}(s^*,t^*)) = 0
\end{equation}
\begin{equation}\label{eq:d_maxdoteq}
\mbold{d}_{\max} \cdot (\mbold{p} - \mbold{X}(s^*,t^*)) = 0
\end{equation}
By solving \req{eq:d_mindoteq}, $ t^* $ is described as
\begin{equation}\label{eq:t*_eq}
t^* = \mbold{d}_{\min} \cdot (\mbold{p}-\mbold{X}(s^*))
\end{equation}
By using \req{eq:t*_eq} and solving \req{eq:d_maxdoteq}, $ s^* $ can be determined.

Let $ s_w,s_r,s_u $ be the arc lengths of the lower wire, ridge line, and upper line and let $ \mbold{\omega}_W (s_w ),\mbold{\omega}_R (s_r ),\mbold{\omega}_U (s_u ) $ be vectors to characterize each of them, respectively. From \req{eq:Cond1}, $ s_r,s_u $ can be expressed as functions of $ s_w $: $ s_r (s_w ),s_u (s_w ) $. As mentioned, a two-piece brassiere cup is composed of two developable surfaces $ S_L $ and $ S_U $. Let $ D $ be a set of coordinates of points on a breast, $ D_L = \{\mbold{p}_{L,i} \in D \} $ be a set of points to evaluate the surface $ S_L $, and $ D_U = \{\mbold{p}_{U,i} \in D \} $ be a set of points to evaluated the surface $ S_U $. Note that $ D_U = D \backslash D_L $. Whether a point $ \mbold{p}_k $ is classified to the set of $ D_U $ or the set of $ D_L $ can determined with the length of the nearest generatrix.
